### 2015-06-26 narrative/intro.tex
started to add a story and research challenges in the introduction so everyone can get started writing.

>>>>

We will examine the research challenges from the perspective of the (1) user of the system who is attempting to run an exascale simulation,
(2) the Storage System and I/O layer which needs to negotiate amongst all of the users, and finally (3) the user of the system who is attempting to
understand the data which was produced from their collection of simulations.

From the perspective of the simulation scientist, they want to be able to have knowledge about how much time they will 
put into writing their data, and how much storage space they will be able to get during the lifetime of their simulations. Furthermore, they
would like the ability to get a certain amount of Quality of Service such that they can then make decisions when the expected bandwidth, for example
is less than what they desire. The user will then place in a certain set of rules which the system can make autonomic decisions to help decide what
should be done. In our simple scenario, a user wants to perhaps write 1 PB of data every hour for their checkpoint/restart, and they which to write 500TB of data
every 15 minutes for their analysis and visualization results which have been reduced by using in situ reduction techniques. At this stage, they will ask the system
to write their data, and they would like to get an estimated time which they can then figure out, through a series of rules, whether they want to write out all of the
data or if they want to write none of the data but rather wait for a later time to write or write a reduced amount of data, along with some code container to allow them 
to regenerate the data with a certain level of accuracy. Furthermore, they realize that the analysis data will be saved on either the parallel file system, or the campaign storage,
a longer term storage area with lower bandwidth than the parallel file system, or if some of the data will just go to tape. Each piece of data the user will specify the
time they will want to keep the data round. We want the system to give the users a certain amount of currency in terms of bandwidth, storage space on each level, and latency expectations.
These notions will be fuzzy but they will allow the user to make ad-hoc decisions to figure out what needs to be saved.

Since the data will be a collection of objects placed to the storage system, some of the objects will be broken up into multiple pieces by ``plug-ins'' to the system
which will allow data to be characterized in terms of the most important pieces, and the next level of details. We can think of this as something similar to an Adaptive Mesh Refinement scheme
which keeps track of the places where there are perhaps steep gradients (large errors on the coarser views), and smaller errors.  These then allows us to make decisions about which 
sub-objects to save (all of the data, which will then go to different layers) or just some of the sub-objects?  The research questions are numerous: How does the user specify their intentions? 
How does the user prioritize the different sub-objects of the data? Where does the data go into the storage hierarchy? Does the data get replicated in the lower tiers of the hierarchy? 
When the user specifies the time they want the data saved, how does this get into the storage system?

From the perspective of the storage system, it needs to manage the data from a given user request amongst all of the request and try to optimize the entire system. Today the problem is that
when a user writes there is a tremendous amount of interference from other users on the system who may be writing or reading at the same time. By maiming a certain level of quality of service
the system must potentially lock out users with lower currency they want to place in the reading or writing of their data.  The storage system must also automatically move data from one tier of the
storage to another, without effecting the quality of service that it guarantees at the time of questioning. The storage system must also look at ways to organize data amongst all of the tiers of
storage in one consistent way.

From the perspective of the users who want to read in the data from their simulations, and then operate on this data and possibly write data, we
see that in general these users will be running on much less compute resources than the users who are running the simulation. One of the
important aspects of this class of user is that they want a reduction of latency and they require a certain amount of quality of service as well. 
When someone is doing interactive analysis and expects that the data they read in is about 10s, but it terms into 1,000s, the user typically
tends to either wait another day for doing their analysis, or gets frustrated and reads much less data than they really need to. Furthermore
the user tends to read in just a small sample of the data without much knowledge if they are missing important pieces of the data.

Our research into the storage system and middle ware layers must address many of these challenges including
\begin{enumerate}
\item  How do we describe the user intentions at the API layer and have this communicated down to the middle-ware and storage layers?
\item How do we allow users to define their user defined compression techniques and have this data read back from the storage system layers? Where do we execute the decompression techniques
\item How do we evaluate the tradeoffs at runtime to guide data placement, including the movement of data across the network, across the
different storage tiers? 
\item Can we use different forms of learning techniques as daemons on the system to perform data migration from one storage tier to another?
For example, if we see that a user is looking at one time slice after another for a certain object in their dataset which is in the slower tiers of 
the hierarchy, do we automatically propane up the data which has not been requested in the hope that this will be requested data?
\item Can we understand the true need of campaign storage and understand the possible impact of the campaign storage if we run a 
hadoop-like file-system instead of a lustre/gpfs file system?
\item Can we limit the amount of data duplication? Data space is going to be very constrained on the exascale system so we must ensure that
minimal copies are made of data, and when data is duplicated, they are removed through a garbage collection routine.
\item Can we build a model to give us the time estimates during the reading and writing phases, so that rules can be in place from the user
perspective to make adaptive decisions. For example, if the file system says that reading will take 3 months, users can they place in rules to
then read in a subset of data, and they can understand which data can be read quickly and which pieces will take more time.
\item Can we understand how to place code in the system which will allow data-regeneration to take place.

\end{enumerate}
